Title of the Master Thesis

### 2016-03-06 Master Thesis/synopsis.tex
Start proof to 2.2

\begin{lemma}\label{2.2}
Let $K$ be henselian with respect to two different valuations $w_1,w_2\in |\operatorname{Spv}(K)|$. Then $K$ is algebraically closed or $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K),\ v(w_1)=v(w_2)$ and $k(v(w_1))$ is separably closed. In the last case we have $\operatorname{cd}(G_K)\leq 2$.
\end{lemma}

>>>>

\begin{lemma}\label{2.2}
Let $K$ be henselian with respect to two different valuations $w_1,w_2\in |\operatorname{Spv}(K)|$. Then $K$ is algebraically closed or $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K),\ v(w_1)=v(w_2)$ and $k(v(w_1))$ is separably closed. Furthermore, we have $\operatorname{cd}(G_K)\leq 2$.
\end{lemma}

\begin{proof}
Assume that $K$ is not algebraically closed, i.e. $G_K\neq 1$ and set $v_i = v(w_i)$. If $v_1\neq v_2$, by the Theorem of F.K. Schmidt we have $G_{v_1}\cap G_{v_2} = 1 \neq G_K$, a contradiction. Therefore $v_1 = v_2$.

Now $k(v_1) = k(v_2)$ is henselian with respect to both $w_1\mod v_1$ and $w_2\mod v_2$. Again by the Theorem of F.K. Schmidt we get $G_{k(v_1)} = 1$, hence $k(v_1)$ is separably closed.

The second assertion follows from the first and from [K2], §5, Theorem 1.
\end{proof}
